Opening Restaurants During COVID-19 Can Prove Beneficial for Restaurant Revenue in the GTA

### 2021-02-27 outputs/Paper.Rmd
update

```{r ttest, echo=FALSE}
#install.packages("broom")
library(broom)
revenue_c <- control_data$Q13
revenue_t <- treated_data$Q13
t<-t.test(revenue_t, revenue_c)
m<-tidy(t, digits=1)
m%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    mean_of_Treated=estimate1,
    mean_of_Control=estimate2
  )%>%
  kableExtra::kbl(caption = "T Test on the Restaurant's revenue") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()

>>>>

```{r ttest, echo=FALSE}
#install.packages("broom")
library(broom)
revenue_c <- control_data$Q13
revenue_t <- treated_data$Q13
t<-t.test(revenue_t, revenue_c)
m<-tidy(t, digits=1)
m%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    mean_of_Treated=estimate1,
    mean_of_Control=estimate2
  )%>%
  kableExtra::kbl(caption = "T Test on the Restaurant's revenue") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling( )
